A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-31 1_intro.tex
cite cura

One promising direction to avoid over- and underfills is to employ toolpath with adaptive width.
Wire and arc additive manufacturing supports a wide range of widths~\cite{Ding2014,Xiong2019},
which led \citeauthor{Ding2016a} to develop a toolpath strategy which produces a width variation typically lower than a factor of $3$, but is sometimes far greater~\cite{Ding2016a}.
However, the limitations on width imposed by the hardware system are far greater for FDM.
A nozzle of \SI{0.4}{\milli\meter} will typically start to cause fluttered extrusion around lines narrower than \SI{0.3}{\milli\meter} and lines will start to bulge upward if they are wider than the flat part of the nozzle, which is typically \SI{1.0}{\milli\meter}.
%Therefore, a limited range of widths is required by the hardware system.

The current state-of-the-art for FDM printing developed by \citeauthor{Jin2017JMS} is employing a strategy which alters the widths of the centermost beads at most by a factor of $2$~\cite{Jin2017JMS}.
See \cref{intro_wedge_centered}.
Still, controlling the extrusion width through movement speed changes or through volumetric flow control (e.g. linear advance) yields diminishing accuracy for deposition widths farther away from the nozzle size,
since process parameters such as nozzle temperature are optimized for beads with the nozzle size.
Moreover, reducing the variation in width is beneficial for limiting the variation in mechanical properties of the resulting product, meaning it conforms better to a simulation which employs a heterogeneity assumption.
Therefore, a narrower range of widths is desirable.

>>>>

One promising direction to avoid over- and underfills is to employ toolpath with adaptive width.
\citeauthor{Ding2016a} developed a toolpath strategy which produces a width variation typically lower than a factor of $3$, but is sometimes far greater~\cite{Ding2016a}. This toolpath strategy was applied to wire and arc additive manufacturing~\cite{Ding2014,Xiong2019},
However, the allowable width variation for FDM systems is much narrower.
A nozzle of \SI{0.4}{\milli\meter} will typically start to cause fluttered extrusion around lines narrower than \SI{0.3}{\milli\meter} and lines will start to bulge upward if they are wider than the flat part of the nozzle, which is typically \SI{1.0}{\milli\meter}.
%Therefore, a limited range of widths is required by the hardware system.

The current state-of-the-art for FDM printing developed by \citeauthor{Jin2017JMS} employs a strategy which alters the widths of the centermost beads at most by a factor of $2$~\cite{Jin2017JMS},
which is similar to the strategy employed by the open source industry standard software package Ultimaker Cura~\cite{cura}.
See \cref{intro_wedge_centered}.
Still, controlling the extrusion width through movement speed changes or through volumetric flow control (e.g. linear advance) yields diminishing accuracy for deposition widths farther away from the nozzle size,
since process parameters such as nozzle temperature are optimized for beads with the nozzle size.
Moreover, reducing the variation in width is beneficial for limiting the variation in mechanical properties of the resulting product, meaning it conforms better to a simulation which employs a homogeneity assumption.
Therefore, a narrower range of widths is desirable.
